BareTag Tool-Tracker\\ {\footnotesize {Team 3 - University of Massachusetts Amherst Senior Design Project 2025 }}

### 2024-10-21 draft.tex
changes

\subsection{Tag}\label{AA}
The Tag refers to the trackable device that will be attached to the tools 
on a worksite. The goal is for the Tags to be less than 31.9mm2, which is 
of a similar size to the Apple Airtag. The thickness of the Tags is aimed 
to be under 16mm, with the primary contributor to this size being the 
pouch cell 290mAh Lithium Polymer battery. The peak current draw of the 
Tag is 45mA and is out of the range that a coin cell could support, 
which led to the decision to use a LiPo that fits within our area size 
goals at 25 mm x 28mm. We are aiming for a one year battery life.
The primary part of the Tag is the Qorvo DWM3001C. This module is driven 
by the nRF52833 MCU, and includes BLE, UWB, and accelerometer 
functionality. The DWM3001 provides UWB functionality and has an 
integrated PCB antenna which requires a keep-out zone in the Tag. 
BLE is provided by the nRF52833. This MCU is built on an ARM Cortex 
M4 and operates in the 2.4GHz band. This MCU is programmable over 
JTAG and thus requires a JTAG interface to be added to the Tag PCBs. 
The accelerometer is the LIS12DH, and is used to wake up the module 
upon motion detection. The module will set the interrupt pin on the 
DWM3001 high when there is motion detected. Otherwise, the Tag is in a 
low power mode to save battery life and is not receiving UWB pings. 
Therefore, before the tag goes to sleep the location needs to be checked 
to determine the resting location. The Tag has the BLE radio turned off 
until it exits the UWB perimeter, at which point an interrupt pin turns 
it on to integrate into the Apple Find My network. At this point, the 
UWB module turns off to conserve power. The accelerometer still regulates 
the power mode of the Tag depending on motion to conserve power. This 
device draws a lot of concepts from ECE 523 and ECE 304, both of which 
have a heavy focus on minimizing power consumption via software and 
component selection. The TPS79933 voltage regulator has an output of 
3.3V when the input voltage is over 3.475V. This component is used in 
both the Tags and Anchors as both devices operate on a 3.7V input battery 
with 3.3V ideal operating voltage.

\subsection{Anchor}
There needs to exist at least 3 anchors for the coordinates to be 
transmitted to the user. This is performed through multilateration. 
The Anchors use the same Qorvo DWM3001C modules as on the Tags as all 
of the submodules have a use case here too. The Anchors use UWB to ping 
the Tag and determine its location within the area defined by the 
proximity of the other anchors. They operate on this data using the 
nRF52833 MCU and send it to a host device over LoRaWAN. The RYLR998 
LoRa module in the Anchors operates within the required range for 
LoRaWAN of 902.3 to 914.9 MHz. This module communicates with the MCU 
via UART. The use of these LoRa modules means that the Host Device does 
not need to be exactly on the site of the construction due to the 
kilometers of range that LoRa supports. We will build the LoRaWAN 
protocol on top of LoRa using the nRF52833 MCU. The use of this MCU 
also means that we can take advantage of the BLE it provides and use 
it for a variety of functions. The GPS coordinates of the Anchors must 
be known in order to get the real-world position of the Tags. We can 
also use BLE to communicate with an anchor to alert that a Tag that is 
in BLE mode has been returned to the UWB-supported area. These features 
result in  more power consumption than the Tags, so a 2.2Ah Lithium Ion 
battery is used. This is possible due to less size constraints for the 
Anchors than of the Tag. The size of the Anchor is not a specification 
that matters, however they will be able to be mounted on posts or stuck 
in different site locations depending on the desired use and area to cover.
As stated before, the TPS79933 voltage regulator outputs 3.3V, which is 
the ideal operating voltage for the DWM3001C, along with the LoRa module.

\subsection{Lora Dongle}
This device is a RYLR998 operating over a USB - UART connection with the 
Host Device. It allows for the Host Device to receive the Tag coordinate 
data and operate on it. The size of this device should account for the 
LoRa module plus a USB/UART converter (CP2102N). The size should be similar 
to that of a USB hub, as to not be an inconvenience to have attached to a 
small host device. As such, the dimensions should be approximately 32 x 18 
x 8 mm based on a combination of the component dimensions. 
The Dongle receives power from the CP2102N over a wired USB-C connection, 
so there is no need for an external power supply.

@@

This device can be whatever system a supervisor desires to use as long as 
it can support a physical USB/Serial connection, or do so using adapters. 
The Host Device is backhauling the location data of each Tag to a database 
where the history of the tag locations can be mapped out to determine the 
daily path. This information is also displayed in real time on a map of 
the desired area. The Host Device is also running the macless-haystack 
Find My server, which acts as a means for tracking the Tags that have 
left the UWB area and are now using BLE to integrate with the Apple Find 
My network. The tags all have unique IDs that can be linked to tools or 
equipment, making it easy to parse the data and determine what items have 
been in what location.

>>>>

\subsection{Tag}\label{AA}
The Tag refers to the trackable device that will be attached to the tools 
on a worksite. The goal is for the Tags to be less than $31.9mm^2$, which is 
of a similar size to the Apple Airtag. The thickness of the Tags is aimed 
to be under $16mm$, with the primary contributor to this size being the 
pouch cell $290mAh$ Lithium Polymer battery. The peak current draw of the 
Tag is $45mA$ and is out of the range that a coin cell could support, 
which led to the decision to use a LiPo that fits within our area size 
goals at $25 \ mm \ x \ 28\ mm$. We are aiming for a one year battery life.
\\The primary part of the Tag is the Qorvo DWM3001C. This module is driven 
by the nRF52833 MCU which includes BLE functioality. The DWM3001C also includes, 
UWB and accelerometer modules. The UWB functionality is driven by the DWM3110,
which has an integrated PCB antenna. BLE is provided by the nRF52833. This MCU is built on an ARM Cortex 
M4 and operates at $2.4GHz$. This MCU is programmable over 
SWD and thus requires a corresponding interface to be added to the PCBs. 
The accelerometer is the LIS12DH, and is used to wake up the module 
upon motion detection. The module will set the interrupt pin on the 
DWM3001C high when there is motion detected. Otherwise, the Tag is in a 
low power mode and is not receiving UWB pings. 
Therefore, before the tag goes to sleep the location needs to be checked 
to determine the last known resting location. The Tag has the BLE radio turned off 
until it exits the UWB area, at which point an interrupt pin turns 
it on to integrate the Tag into the Apple Find My network. At this point, the 
UWB module turns off to conserve power. The accelerometer still regulates 
the power mode of the Tag depending on motion to conserve power. This
device draws a lot of concepts from ECE 523 and ECE 304, both of which 
have a heavy focus on minimizing power consumption via software and 
component selection. The TPS79933 voltage regulator has an output of 
$3.3V$ when the input voltage is over $3.475V$. This component is used in 
both the Tags and Anchors as both devices operate on a $3.7V$ battery 
with all modules operating at a $3.3V$ ideal voltage.

\subsection{Anchor}
There needs to exist at least $3$ anchors for the coordinates of a Tag to be 
transmitted to the Host Device, which are calculated through multilateration. 
The Anchors use the same Qorvo DWM3001C modules as on the Tags as all 
of the submodules have a use case here too. The Anchors use UWB to ping 
the Tag and determine its location within the area defined by the 
proximity of the other anchors. They process this data using the 
nRF52833 MCU and send it to a host device over LoRaWAN for coordinate computation. 
The RYLR998 LoRa module in the Anchors operates within the operating range of 
LoRaWAN: $902.3 MHz$ to $914.9 MHz$. This module communicates with the MCU 
via UART. The use of these LoRa modules means that the Host Device does 
not need to be on the site of the construction due to the 
kilometers of range that LoRa supports. We will build the LoRaWAN 
protocol on top of LoRa using the nRF52833 MCUs and Host Device. The use of the nRF52833 
means that we can take advantage of the BLE it provides and use 
it for a variety of functions. The GPS coordinates of the Anchors must 
be known in order to get the real-world position of the Tags, and we can achieve
this through a mobile app that will communicate with the Anchors over Bluetooth. 
This operation will occur during the setup and positioning of the Anchors. We can also
use BLE to communicate with an Anchor to alert that a Tag in 
BLE mode has been returned within range of the Anchors. These features 
result in  more power consumption than the Tags, so a 2.2Ah Lithium Ion 
battery is used. This is possible due to less size constraints for the 
Anchors than of the Tag. The Anchors are not constrained by size, and therefore we 
do not have any strict specifications for its dimensions.
As stated before, the TPS79933 voltage regulator outputs 3.3V, which is 
the ideal operating voltage for the DWM3001C and LoRa module.

\subsection{Lora Dongle}
This device is a RYLR998 operating over a USB/UART connection with the 
Host Device. The Dongle allows the Host Device to receive the Tag location data in 
reference to each Anchor, which the Host Device will then perform the multilateration algorithm on.
The size of this device should be similar 
to that of a commonly used USB hub, as to not be an inconvenience to have attached to a 
small host device. The dimensions will be approximately $32 \ mm\  x \ 18 \ mm \
x \ 8 \ mm$ based on a combination of the Dongle component dimensions, which are the LoRa 
module and a USB/Serial converter. 
\\ The Dongle receives power over USB from the Host Device, which the serial converter will
drop to $3.3V$ for the ideal operating voltage of the LoRa module.

@@

This device can be whatever system a supervisor desires to use as long as 
it can support a USB/Serial connection, or do so using adapters. The Host Device
performs the multilateration algorithms based on the data it receives from the LoRa Dongle.
The calculations get backhauled to a cloud database 
where the history of Tag locations can be mapped out to determine 
daily paths. This information is also displayed locally on a map of 
the desired area. The Host Device is also running the macless-haystack 
server, which acts as a means for tracking the Tags that have 
left the UWB area and are using BLE to integrate with the Apple Find 
My network. The Tags all have unique IDs that can be linked to tools or 
equipment, making it easy to parse the data and determine what items have 
been in what location.
